\section{Introduction}
\label{sec:sec_intro}

The goal of lifelogging is to record and archive all information in one's life. 
This may include all texts, visual information, audio, media activity as well 
as biological data from sensors of one's body. The information would be archived
for the benefit of the lifelogger, and shared with others in various degrees as
controlled by him/her.  With the advances of technology, lifelog is becoming more
 and more popular. Fitness\footnote{http://www.fitbit.com/} tracker as one
 example is wildly worn by people to record  their sports activity, steps taken, distance traveled and calories
 burned.  Using this information, you can choose food, weight, and sleep
 tracking  to manage all aspects of your health.  At the same time, recent 
 technology has make wearable devices more accessible to common people. Google
 glass, and GoPro are just two brilliant example. With their support,  people
 are able to log their visual information.
Compares to other type of lifelog, vision-based lifelogs are more fruitful, and
if using properly, can help make people's life better. Recognizing objects of 
what people are watching can provide essential information about a person's 
activity and situation, thus have far-reaching impact on the application of 
vision in everyday life. The egocentric viewpoints from a wearable camera have
unique advantages in recognizing objects, such as a close view and seeing
objects in their natural positions.

With the vast amount of video and image collected daily, visual lifelog present 
challenges in analysis and store in a form with enable user to retrieved easily 
and extract useful information. Storing and managing videos are more challenging
than other types of data. Videos often followed some structure specification;
hence, prevent us from arbitrary reading and partitionning. Another challenge
is lacking of supported tools for large scale processing. Reseachers uses
special vision processing toolboxes when working with video 

The goal of the project is an application that 
analyses vision-based lifelog video and enable user to retrieve in low
latency manner. In this project, we analyses and proposes an approach for using
big data framework in video processing. We also implement a PeopleCounting
application as a case study. Experiment result shows that our application
achieved good accuracy and promising performance with speedup of 5 comparing to
traditional approach - frame-base Matlab application.

This paper is organized as follows. Section 2 surveys related work on video
processing at large scale. Section 3 gives an overview of opportunities
and challenges when using big data framework for video processing. Section 4
describes our design of large scale video processing stack and our
implementation of PeopleCounting application as a case study. We evaluate
accuracy and efficiency of our implementation in Section 5, and conclude in
Section 6.
